Approximation as Differentiation

### 2025-06-08 main/first-order.tex
How does the lattice of approximants in Fam(LatGal) actually get set up?

The goal now is to equip the interpretation of a (first-order) program with a Galois connection relating
approximations of its inputs to approximations of its output. Since the specific lattices of approximations
depend on the value being approximated, the semantics of every type $\tau$ must have both a conventional
component as well as an approximating component, i.e.~a set $X$ which serves as the usual interpretation of
$\tau$, plus an associated lattice of approximations $\partial X(x)$ for every point $x \in X$. The semantics
of an expression $e$ of type $\sigma$ with a single free variable of type $\tau$ (with $\tau$ and $\sigma$
denoting $X$ and $Y$) must then also have two components: a function $f: X \to Y$ giving the conventional
interpretation of $e$, plus a family of Galois connections $\partial f(x): \partial X(x) \to \partial Y(f(x))$
for every $x \in X$ which can be used for slicing over that expression.

@@

\begin{proposition}
\label{prop:Grothendieck:fam-inherits-products}
If $\cat{C}$ has binary products then so does $\Fam(\cat{C})$.
\end{proposition}

\subsection{Galois Slicing via a Category of Families}
\label{sec:fam:galois-slicing}

@@

\subsection{Automatic Differentiation via a Category of Families}

>>>>

\todo{Rework.} The goal now is to equip the interpretation of a (first-order) program with a Galois connection
relating approximations of its inputs to approximations of its output. Since the specific lattices of
approximations depend on the value being approximated, the semantics of every type $\tau$ must have both a
conventional component as well as an approximating component, i.e.~a set $X$ which serves as the usual
interpretation of $\tau$, plus an associated lattice of approximations $\partial X(x)$ for every point $x \in
X$. The semantics of an expression $e$ of type $\sigma$ with a single free variable of type $\tau$ (with
$\tau$ and $\sigma$ denoting $X$ and $Y$) must then also have two components: a function $f: X \to Y$ giving
the conventional interpretation of $e$, plus a family of Galois connections $\partial f(x): \partial X(x) \to
\partial Y(f(x))$ for every $x \in X$ which can be used for slicing over that expression.

@@

\begin{proposition}
\label{prop:Grothendieck:fam-inherits-products}
\item
\begin{enumerate}
If $\cat{C}$ has (symmetric) monoidal products then $\Fam(\cat{C})$ has (symmetric) monoidal products
$(X, \partial X) \tensor (Y, \partial Y) = (X \times Y, \partial(X \times Y))$ indexed by the Cartesian
product $X \times Y$, where $\partial(X \times Y)(x,y) = \partial X(x) \tensor \partial Y(y)$.
\end{enumerate}
\end{proposition}

\subsection{First-Order Galois Slicing via CHAD}
\label{sec:fam:galois-slicing}

@@

\todo{Show how $\LatGal$ has a lifting monad?}

\subsection{First-Order Automatic Differentiation via CHAD}
